---
title: "TimeSeries_NYC"
author: "ILNY_Group"
date: "6/14/2019"
output: html_document
---

# import required packages
```{r}
library(ggplot2)
library(quantmod)
library(xts)
library(zoo)
library(forecast)
library(fpp)
library(fpp2)
library(dplyr)
library(ggthemes)
library(caret)
library(lattice)
```


# import  dataset
```{r}
library(readxl)
pre <- read.csv("D:/OneDrive/Documents/CU/2019Summer/5900_Capstone/TimeSeriesAnalysis/Data/NYC_predict.csv")
data=pre
data = na.omit(pre)
str(data)
```


# create time series data
### create New York state's hotel occ% time series data
```{r}
OCC_ts = ts(data=pre[[2]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel Room_Count time series data
```{r}
RoomCount_ts = ts(data=pre[[3]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel RevPAR time series data
```{r}
RevPAR_ts = ts(data=pre[[4]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel Room_Sold time series data
```{r}
RoomSold_ts = ts(data=pre[[5]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel ADR time series data
```{r}
ADR_ts = ts(data=pre[[6]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel Room_Revenue time series data
```{r}
RoomRev_ts = ts(data=pre[[7]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's Monthly_Visiation time series data
```{r}
visit_ts = ts(data=data[[9]], start=c(2014, 1), end=c(2018, 12), frequency = 12)
```
### create New York state's Monthly_Spending time series data
```{r}
spend_ts = ts(data=data[[10]], start=c(2014, 1), end=c(2018, 12), frequency = 12)
```


# trend and seasonality analysis
### OCC
```{r}
OCC_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### Room_Count
```{r}
RoomCount_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### RevPAR
```{r}
RevPAR_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### Room_Sold
```{r}
RoomSold_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### ADR
```{r}
ADR_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### Room_Revenue
```{r}
RoomRev_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```


# prediction (time series analysis)
### predict OCC
```{r}
model_auto_OCC = auto.arima(y = OCC_ts, stepwise = F,approximation = F)
model_auto_forecas_OCC = forecast(model_auto_OCC,h=6)
model_auto_forecas_OCC
autoplot(model_auto_forecas_OCC,PI=F)
```
### predict Room_Count
```{r}
model_auto_RoomCount = auto.arima(y = RoomCount_ts, stepwise = F,approximation = F)
model_auto_forecas_RoomCount = forecast(model_auto_RoomCount,h=6)
model_auto_forecas_RoomCount
autoplot(model_auto_forecas_RoomCount,PI=F)
```
### predict RevPAR
```{r}
model_auto_RevPAR = auto.arima(y = RevPAR_ts, stepwise = F,approximation = F)
model_auto_forecas_RevPAR = forecast(model_auto_RevPAR,h=6)
model_auto_forecas_RevPAR
autoplot(model_auto_forecas_RevPAR,PI=F)
```
### predict Room_Sold
```{r}
model_auto_RoomSold = auto.arima(y = RoomSold_ts, stepwise = F,approximation = F)
model_auto_forecas_RoomSold = forecast(model_auto_RoomSold,h=6)
model_auto_forecas_RoomSold
autoplot(model_auto_forecas_RoomSold,PI=F)
```
### predict ADR
```{r}
model_auto_ADR = auto.arima(y = ADR_ts, stepwise = F,approximation = F)
model_auto_forecas_ADR = forecast(model_auto_ADR,h=6)
model_auto_forecas_ADR
autoplot(model_auto_forecas_ADR,PI=F)
```
### predict Room_Revenue
```{r}
model_auto_RoomRev = auto.arima(y = RoomRev_ts, stepwise = F,approximation = F)
model_auto_forecas_RoomRev = forecast(model_auto_RoomRev,h=6)
model_auto_forecas_RoomRev
autoplot(model_auto_forecas_RoomRev,PI=F)
```


