---
title: "Economic_Impact_Prediction"
author: "ILNY_Group"
date: "6/14/2019"
output: html_document
---

# import required packages
```{r}
library(ggplot2)
library(quantmod)
library(xts)
library(zoo)
library(forecast)
library(fpp)
library(fpp2)
library(dplyr)
library(ggthemes)
library(caret)
library(lattice)
```


# import  dataset
```{r}
library(readxl)

pre =NYS_predict
pre = na.omit(NYS_predict)
str(pre)
```


# create time series data
### create New York state's hotel occ% time series data
```{r}
OCC_ts = ts(data=pre[[2]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
```{r}
OCC_ts
```

### create New York state's hotel Room_Count time series data
```{r}
RoomCount_ts = ts(data=pre[[3]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel RevPAR time series data
```{r}
RevPAR_ts = ts(data=pre[[4]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel Room_Sold time series data
```{r}
RoomSold_ts = ts(data=pre[[5]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel ADR time series data
```{r}
ADR_ts = ts(data=pre[[6]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's hotel Room_Revenue time series data
```{r}
RoomRev_ts = ts(data=pre[[7]], start=c(2014, 1), end=c(2019, 4), frequency = 12)
```
### create New York state's Monthly_Visiation time series data
```{r}
visit_ts = ts(data=data[[9]], start=c(2014, 1), end=c(2018, 12), frequency = 12)
```
### create New York state's Monthly_Spending time series data
```{r}
spend_ts = ts(data=data[[10]], start=c(2014, 1), end=c(2018, 12), frequency = 12)
```


# trend and seasonality analysis
### OCC
```{r}
OCC_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### Room_Count
```{r}
RoomCount_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### RevPAR
```{r}
RevPAR_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### Room_Sold
```{r}
RoomSold_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### ADR
```{r}
ADR_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```
### Room_Revenue
```{r}
RoomRev_ts%>%
  stl(s.window = 'periodic')%>%
  autoplot()
```


# prediction (time series analysis)
### predict OCC
```{r}
model_auto_OCC = auto.arima(y = OCC_ts, stepwise = F,approximation = F)
model_auto_forecas_OCC = forecast(model_auto_OCC,h=6)
model_auto_forecas_OCC
autoplot(model_auto_forecas_OCC,PI=F)
```
```{r}
class(model_auto_forecas_OCC)
```


### predict Room_Count
```{r}
model_auto_RoomCount = auto.arima(y = RoomCount_ts, stepwise = F,approximation = F)
model_auto_forecas_RoomCount = forecast(model_auto_RoomCount,h=6)
model_auto_forecas_RoomCount
autoplot(model_auto_forecas_RoomCount,PI=F)
```
### predict RevPAR
```{r}
model_auto_RevPAR = auto.arima(y = RevPAR_ts, stepwise = F,approximation = F)
model_auto_forecas_RevPAR = forecast(model_auto_RevPAR,h=6)
model_auto_forecas_RevPAR
autoplot(model_auto_forecas_RevPAR,PI=F)
```
### predict Room_Sold
```{r}
model_auto_RoomSold = auto.arima(y = RoomSold_ts, stepwise = F,approximation = F)
model_auto_forecas_RoomSold = forecast(model_auto_RoomSold,h=6)
model_auto_forecas_RoomSold
autoplot(model_auto_forecas_RoomSold,PI=F)
```
### predict ADR
```{r}
model_auto_ADR = auto.arima(y = ADR_ts, stepwise = F,approximation = F)
model_auto_forecas_ADR = forecast(model_auto_ADR,h=6)
model_auto_forecas_ADR
autoplot(model_auto_forecas_ADR,PI=F)
```
### predict Room_Revenue
```{r}
model_auto_RoomRev = auto.arima(y = RoomRev_ts, stepwise = F,approximation = F)
model_auto_forecas_RoomRev = forecast(model_auto_RoomRev,h=6)
model_auto_forecas_RoomRev
autoplot(model_auto_forecas_RoomRev,PI=F)
```
```{r}
model_auto_Visitation = auto.arima(y = visit_ts, stepwise = F,approximation = F)
model_auto_forecas_Visitation = forecast(model_auto_Visitation,h=6)
model_auto_forecas_Visitation
```
```{r}
model_auto_Spend = auto.arima(y = spend_ts, stepwise = F,approximation = F)
model_auto_forecas_Spend = forecast(model_auto_Spend,h=6)
model_auto_forecas_Spend
```


# identify target variables
### scatter plot 1: Monthly_Visitation V.S. Monthly_Spending
```{r}
ggplot(data=data, aes(x= Monthly_Visitation, y=Monthly_Spending))+geom_point()+geom_smooth()
```
### scatter plot 2: Monthly_Visiation V.S. Room_Revenue
```{r}
ggplot(data=data, aes(x= Room_Revenue, y= Monthly_Visitation))+geom_point()+geom_smooth()
```
### scatter plot 3: Monthly_Visiation V.S. Room_Sold
```{r}
ggplot(data=data, aes(x= Room_Sold, y= Monthly_Visitation))+geom_point()+geom_smooth()
```
### scatter plot 4: Monthly_Spending V.S. Room_Sold
```{r}
ggplot(data=data, aes(x= Room_Sold, y=Monthly_Spending))+geom_point()+geom_smooth()
```
### scatter plot 5: Monthly_Spending V.S. Room_Revenue
```{r}
ggplot(data=data, aes(x= Room_Revenue, y=Monthly_Spending))+geom_point()+geom_smooth()
```


# prediction(linear regression anlysis)
### Split Data
```{r}
visitation=data %>% select(Monthly_Visitation,Room_Sold,ADR,Room_Count,RevPAR,Room_Revenue,OCC)
spending=data %>% select(Monthly_Spending,Room_Sold,ADR,Room_Count,RevPAR,Room_Revenue,OCC)

set.seed(1706)
split_1 = createDataPartition(y=visitation$Monthly_Visitation,p = 0.7,list = F,groups = 10)
train_visit = visitation[split_1,]
test_visit = visitation[-split_1,]

split_2 = createDataPartition(y=spending$Monthly_Spending ,p = 0.7,list = F,groups = 10)
train_spend = spending[split_2,]
test_spend = spending[-split_2,]
```
### Linear Regression- visitation (monthly)
```{r}
lm_visit = lm(Monthly_Visitation~.,train_visit)
predLm_visit = predict(lm_visit,newdata=test_visit)
RMSELm_visit = sqrt(mean((predLm_visit - test_visit$Monthly_Visitation)^2))
RMSELm_visit
```
### Linear Regression-spending (monthly)
```{r}
lm_spend = lm(Monthly_Spending~.,train_spend)
predLm_spend = predict(lm_spend,newdata=test_spend)
RMSELm_spend = sqrt(mean((predLm_spend - test_spend$Monthly_Spending)^2))
RMSELm_spend
```
### Insert New Dataset (Prediction)
```{r}
preData = Prediction.New.Dataset.for.Spending.and.Visitation
```
### Predict
```{r}
Prelm_spend_new = predict(lm_spend, newdata = preData)
Prelm_spend_new
```
```{r}
Prelm_visitation_new = predict(lm_visit, newdata = preData)
Prelm_visitation_new
```

```{r}
wholetable=cbind(preData,Prelm_spend_new,Prelm_visitation_new)
wholetable
```
### Plot (!!!The Month is Not Right)
```{r}
pre_spend_ts = ts(data=wholetable$Prelm_spend_new, start=c(2019, 5), end=c(2019, 10), frequency = 12)
pre_visitation_ts = ts(data=wholetable$Prelm_visitation_new, start=c(2019, 5), end=c(2019, 10), frequency = 12)
autoplot(pre_spend_ts)
autoplot(pre_visitation_ts)
```


# prediction(linear regression anlysis)
### Split Data
```{r}
train_v = window(visit_ts,end=c(2017,09))
test_v = window(visit_ts, start=c(2017,10))

train_s = window(spend_ts,end=c(2017,09))
test_s = window(spend_ts, start=c(2017,10))
```
### time series model(visitation)
```{r}
model_auto_v = auto.arima(y = train_v, stepwise = F,approximation = F)
model_auto_forecast_v = forecast(model_auto_v,h=15)
```
### time series model(spending)
```{r}
model_auto_s = auto.arima(y = train_s, stepwise = F,approximation = F)
model_auto_forecast_s = forecast(model_auto_s,h=15)
```
### check accuracy
```{r}
print("accuracy of Monthly_Visitation's prediction")
accuracy(model_auto_forecast_v,x=test_v)

print("accuracy of Monthly_Spending's prediction")
accuracy(model_auto_forecast_s,x=test_s)
```

### New Dataset with prediction data

```{r}
write.csv(newdataset_prediction)
```

# export cleaned data
```{r}
write.csv(model_auto_forecas_RoomSold,'D:\\OneDrive\\Documents\\CU\\2019Summer\\5900_Capstone\\TimeSeriesAnalysis\\Predicted data\\predicted_RoomSold.csv', row.names = F )
write.csv(model_auto_forecas_OCC,'D:\\OneDrive\\Documents\\CU\\2019Summer\\5900_Capstone\\TimeSeriesAnalysis\\Predicted data\\predicted_OCC.csv', row.names = F )
write.csv(model_auto_forecas_RoomRev,'D:\\OneDrive\\Documents\\CU\\2019Summer\\5900_Capstone\\TimeSeriesAnalysis\\Predicted data\\predicted_RoomRev.csv', row.names = F )
write.csv(model_auto_forecas_ADR,'D:\\OneDrive\\Documents\\CU\\2019Summer\\5900_Capstone\\TimeSeriesAnalysis\\Predicted data\\predicted_ADR.csv', row.names = F )
write.csv(model_auto_forecas_RevPAR,'D:\\OneDrive\\Documents\\CU\\2019Summer\\5900_Capstone\\TimeSeriesAnalysis\\Predicted data\\predicted_RevPAR.csv', row.names = F )
write.csv(model_auto_forecas_RoomCount ,'D:\\OneDrive\\Documents\\CU\\2019Summer\\5900_Capstone\\TimeSeriesAnalysis\\Predicted data\\predicted_RoomCount.csv', row.names = F )
```